---
title: "hw06"
author: "Caroline Seip"
date: '2018-11-08'
output: github_document
---

For this assignment I will be performing two tasks. First I will explore character data by reading and completing the exercises in the Strings chapter. Secondly I will write a function to convert Fahrenheit to Celsius.

#Table of Contents
- Loading packages
- Character Data
- Writing Functions

#Loading packages

Load the required packages:

```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(stringi))
suppressPackageStartupMessages(library(testthat))
```

#Task 1: Character Data

##Read and work the exercises in the Strings chapter

###Find the stringi function that:

####Counts the number of words in a sentence

Using `strsplit`:

```{r}
#Make a string of words, aka a sentence
string <- "Caribou are classified as a threatened species in Canada"
#Split the sentence by spaces, then find the length
sapply(strsplit(string, " "), length)
```
There are 9 words in the sentence.

Using `stri_count_fixed`:

```{r}
#Count the number of spaces in the sentence, plus one because there will always be 
#one more word in a sentence than the number of spaces
stri_count_fixed(string, " ") + 1
```
There are 9 words in the sentence

####Finds duplicated strings

Using `stri_duplicated`:

```{r}
stri_duplicated(c("n", "a", "t", "h", "a", "n"), fromLast = FALSE)
```
There are two duplicate letters in the name Nathan, "a" and "n".

####Generate random text

Using `stri_rand_lipsum`:

```{r}
#Generate one paragraph of random lorem ipsum text, don't start with lorem ipsum
stri_rand_lipsum(1, start_lipsum = FALSE)
```

###How do you control the language that 'stri_sort' uses for sorting?

Specifying the `locale` in the `stri_sort` function allows us to change the language, for example:

```{r}
#Sort letters, using American english
stri_sort(letters, locale="en_US")
```

```{r}
#Sort letters, using Lithuanian
stri_sort(letters, locale="lt_LT")
```

If we specify Lithuanian, the letter "y" moves to between "i" and "j", instead of between "x" and "z".

#Task 2: Writing Functions

##Converting temperature data from remote wildlife cameras :camera: :bear: :deer:

I have chosen to write a function to convert Fahrenheit to Celsius. This is useful for me because I use remote wildlife cameras that have internal thermometers to report temperature. The default setting on these cameras is Fahreneheit, so if the camera is not set up correctly the temperature will be reported in Fahrenheit, instead of Celsius.

The formula for converting Fahrenheit to Celsius is:

`C= (F-32)*(5/9)`

To test I will convert a commonly seen temperature on the cameras to Celsius (...it's northern Alberta :snowflake:)

```{r}
#The input of 'FtoC' is temperature in Fahrenheit
FtoC <- function(f) {
#F to C formula
  c <- (f-32)*(5/9)
  #FtoC will return the temperature in Celsius
  return(c)
}
#Test the function by converting -30F to C
FtoC(-30)
```
-30F is equal to -34.4C. This was the expected result.

Now let's formally test the function `FtoC` using `testthat`:

32 degrees Fahrenheit should be equal to 0 degrees Celsius

```{r}
test_that("Simple cases work", {
  expect_equal(FtoC(32), 0)
})
```
Seems happy! :smiley:

Now let's try to break the function:

```{r error=TRUE}
FtoC("hello")
```
Great, it doesn't work on character data.

Let's update the `FtoC` function to throw a custom error if the input is not numeric:

```{r error=TRUE}
FtoC <- function (f) {
  if (!is.numeric(f)) {
    stop(paste("Expecting f to be numeric, you gave me",
               typeof(f)))
  }
  (f-32)*(5/9)
}
FtoC("hello")
```
Nice! We have now made a custom error message for the `FtoC` function, so that it will only accept numeric data.


